Model Finding for Recursive Functions in SMT

### 2015-04-28 tex/main.tex
Minor fixes

For solvers, we considered the SMT solver \ziii~\cite{de-moura-bjoerner-2008}, 
which runs both heuristic methods for quantifier instantiation,
as well as methods for finding models for quantified formulas~\cite{GeDeM-CAV-09}.
We also considered three configurations of \cvc~\cite{barrett-et-al-2011} which we will refer to as {\bf cvc4}, {\bf cvc4+f} and {\bf cvc4+i}.
The default configuration {\bf cvc4} runs heuristic quantifier instantiation, but does not include techniques for finite model finding.
The configuration {\bf cvc4+f} runs a finite model finding procedure~\ref{ReyEtAl-1-RR-13}.
The last configuration {\bf cvc4+i} incorporates techniques for automating inductive reasoning in SMT~\ref{reynolds-kuncak-2015}.

>>>>

For solvers, we considered the SMT solver \ziii~\cite{de-moura-bjoerner-2008}, 
which runs both heuristic methods for quantifier instantiation,
as well as methods for finding models for quantified formulas~\cite{GeDeM-CAV-09}.
We also considered three configurations of \cvc~\cite{barrett-et-al-2011} which we will refer to as {\bf cvc4}, {\bf cvc4+f} and {\bf cvc4+i}.
The default configuration {\bf cvc4} runs heuristic quantifier instantiation, but does not include techniques for finite model finding.
The configuration {\bf cvc4+f} runs a finite model finding procedure~\cite{ReyEtAl-1-RR-13}.
The last configuration {\bf cvc4+i} incorporates techniques for automating inductive reasoning in SMT~\cite{reynolds-kuncak-2015}.
